Memory-aware Adaptive Scheduling of Scientific Workflows On Heterogeneous Architectures\\

### 2024-10-10 main.tex
some remaining edits in rel. work I forgot to commit yesterday

    PEFT (Predict earliest finish time) algorithm~\cite{arabnejad2014list} is a HEFT variant that computes an Optimistic
    Cost Table OCT.
    OCT is computed per task-processor pair and stores the longest shortest path from this task to the target task, if this
    processor is chosen for this task.
    Ranking is based on OCT values.
    Processor choice stage minimizes the Optimistic EFT, which is EFT plus the the longest path to the exit node for each task.

>>>>

    PEFT (Predict earliest finish time)~\cite{arabnejad2014list} is a HEFT variant that computes an Optimistic
    Cost Table (OCT).
    The OCT is computed per task-processor pair and stores the longest shortest path from this task to the target task if this
    processor is chosen for this task.
    Ranking is based on OCT values.
    The processor choice stage minimizes the optimistic EFT, which is EFT plus the longest path to the exit node for each task.
